Conversations in time: interactive visualization to explore structured temporal data

### 2020-07-22 tsibbletalk.Rmd
brief draft on tsibble and its workflow

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- familyname: Wang
  othernames: Earo
  address: Department of Statistics, The Univeristy of Auckland, New Zealand
  email: earo.wang@auckland.ac.nz
  correspondingauthor: true
- familyname: Cook
  othernames: Dianne
  address: Department of Econometrics and Business Statistics, Monash University, Australia
  email: dicook@monash.edu
abstract: "A brief summary of our ideas"
keywords: ""
blind: false
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
output:
  UOARmdTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    number_sections: yes
    citation_package: biblatex
    dev: "pdf"
---

@@

# Background

@@

* {ggobi} and {xggobi}
* {cranvas} and {cranvastime}
* [crossfilter.js](http://crossfilter.github.io/crossfilter/)
* {crosstalk} and html widgets

@@

* {tsibble}
* and tsibble-centered workflow

>>>>

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The Univeristy of Auckland
  address:
  - line 1
  - line 2
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash Univeristy
  address:
  - line 1
  - line 2
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

# Background and motivation

@@

* {ggobi} and {xggobi}
* {cranvas} and {cranvastime}
* [crossfilter.js](http://crossfilter.github.io/crossfilter/) & [dc.js](https://dc-js.github.io/dc.js/)
* {crosstalk} and html widgets

@@

The \CRANpkg{tsibble} package extends the `data.frame` and \CRANpkg{tibble} structure to represent temporal data in tidy format [cite]. A tsibble consists of *index*, *key*, and other measured variables in one data frame. The *index* column holds time-based indices. The *key* column(s) uniquely identifies a collection of related observational units during a period of time defined by *index*. They are "sticky" columns to a `tsibble` over the course of transformation.

The \CRANpkg{feasts} and \CRANpkg{fable} packages, part of the **tidyverts** suite, aim to make time series analysis easier. They provide analytical and forecasting tools for the tsibble data structure, generating tsibble-centered workflow. Functions, such as `features()` and `model()`, summarise a sequence of indexed values down to a single statistic or model by every observational unit. The output is a normal table, where each row corresponds to an observational unit denoted by "key". In the context of relational databases, the "key" acts like a foreign key in a reduced form of tsibble, while the index and key together operates like a primary key.

At the early stage of exploratory temporal data analysis, time series plots and scatterplots goes hand by hand. (insert figures below)
